Step 13: Marginal Effects Analysis with Multiple Imputation

### 2025-09-08 reanalysis-13-marginal_effects.qmd
ame

  pdr_any_tx = list(
    name = "PDR on any treatment",
    subset_condition = expression(PDR == "Present" & 
                                 (PRP_flag == 1 | anti_VEGF == 1 | 
                                  focal_laser_flag == 1 | other_inject == 1)),
    description = "Patients with PDR receiving any treatment"
  ),

  pdr_anti_vegf_only = list(
    name = "PDR on anti-VEGF only",
    subset_condition = expression(PDR == "Present" & 
                                 PRP_flag == 0 & anti_VEGF == 1 & 
                                 focal_laser_flag == 0 & other_inject == 0),
    description = "Patients with PDR receiving anti-VEGF only"
  ),

  pdr_prp_only = list(
    name = "PDR on PRP only",
    subset_condition = expression(PDR == "Present" & 
                                 PRP_flag == 1 & anti_VEGF == 0 & 
                                 focal_laser_flag == 0 & other_inject == 0),
    description = "Patients with PDR receiving PRP only"
  )
)

>>>>

  pdr_any_tx = list(
    name = "PDR on any treatment",
    subset_condition = expression(dr_severity == "PDR" & 
                                 (PRP_flag == 1 | anti_VEGF == 1 | 
                                  focal_laser_flag == 1 | other_inject == 1)),
    description = "Patients with PDR receiving any treatment"
  ),

  pdr_anti_vegf_only = list(
    name = "PDR on anti-VEGF only",
    subset_condition = expression(dr_severity == "PDR" & 
                                 PRP_flag == 0 & anti_VEGF == 1 & 
                                 focal_laser_flag == 0 & other_inject == 0),
    description = "Patients with PDR receiving anti-VEGF only"
  ),

  pdr_prp_only = list(
    name = "PDR on PRP only",
    subset_condition = expression(dr_severity == "PDR" & 
                                 PRP_flag == 1 & anti_VEGF == 0 & 
                                 focal_laser_flag == 0 & other_inject == 0),
    description = "Patients with PDR receiving PRP only"
  )
)
